### 2020-03-06 README.Rmd
Done create_focal_vs_comp()

```{r}
census_df1 <- bw_2008
# we need to filter out the resprouts
census_df2 <- bw_2014 %>% filter(!str_detect(codes,'R'))
id <- "treeID"

@@

# ID which points are in buffer and which are not
index <- st_intersects(bw_growth_df, bw_buffer, sparse = FALSE)
bw_growth_df <- bw_growth_df %>% 
  mutate(buffer = index[,1])

@@

# ID which points are in buffer and which are not
index <- st_intersects(scbi_growth_df, scbi_buffer, sparse = FALSE)
scbi_growth_df <- scbi_growth_df %>% 
  mutate(buffer = index[,1])

@@

```{r}
bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = 100, k = 28, 
  xOffset = 0.5, yOffset = 0.99999,
  verbose = FALSE
)

# Add foldID to data
bw_growth_df <- bw_growth_df %>% 
  mutate(
    foldID = bw_cv_grid$foldID,
    foldID = factor(foldID)
  )

# Visualize grid
bw_cv_grid$plots +
  geom_sf(data = bw_growth_df, aes(col=foldID), size = 0.1)
```

@@

```{r}
scbi_cv_grid <- spatialBlock(
  speciesData = scbi_growth_df, theRange = 100, k = 28, yOffset = 0.6, verbose = FALSE
)

# Add foldID to data
scbi_growth_df <- scbi_growth_df %>% 
  mutate(
    foldID = scbi_cv_grid$foldID,
    foldID = factor(foldID)
  )

# Visualize grid
scbi_cv_grid$plots +
  geom_sf(data = scbi_growth_df, aes(col=foldID), size = 0.1)
```

@@

Next we specify the growth model we want. We will model growth as a function of tree identiy, size, and the size and identiy of its neighbors. The model can be run on different grouping of individuals (e.g., based on species or trait groupings). It can also be run with different measures of competition.

@@

```{r}
bw_specs <- get_model_specs(bw_2008, 3, 'trait_group')
bw_specs

scbi_specs <- get_model_specs(scbi_2013, 3, 'sp')

Next we create the `focal_vs_comp` object which connects each tree to the trees in its competitive neighborhood (with `max_dist`). This required `growth_df`, `max_dist`, `cv_fold_size`, and `model_specs` as inputs.

```{r}
bw_focal_vs_comp <- create_focal_vs_comp(bw_growth_df, max_dist, cv_fold_size, bw_specs)
scbi_focal_vs_comp <- create_focal_vs_comp(scbi_growth_df, max_dist, cv_fold_size, scbi_specs)

>>>>

```{r}
census_df1 <- bw_2008
# we need to filter out the resprouts
census_df2 <- bw_2014 %>% 
  filter(!str_detect(codes, 'R'))
id <- "treeID"

@@

# ID which points are in buffer and which are not
buffer_index <- !st_intersects(bw_growth_df, bw_buffer, sparse = FALSE)
bw_growth_df <- bw_growth_df %>% 
  mutate(buffer = as.vector(buffer_index))

@@

# ID which points are in buffer and which are not
buffer_index <- st_intersects(scbi_growth_df, scbi_buffer, sparse = FALSE)
scbi_growth_df <- scbi_growth_df %>% 
  mutate(buffer = as.vector(buffer_index))

@@

```{r}
set.seed(76)
bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = 100, verbose = FALSE,
  # Some guess work in figuring this out:
  k = 28, xOffset = 0.5, yOffset = 0
)

# Add foldID to data
bw_growth_df <- bw_growth_df %>% 
  mutate(
    foldID = bw_cv_grid$foldID
  )

# Visualize grid. Why does fold 19 repeat?
bw_cv_grid$plots +
  geom_sf(data = bw_growth_df %>% sample_frac(0.2), aes(col=factor(foldID)), size = 0.1)

# Remove weird folds with no trees in them from viz above
bw_growth_df <- bw_growth_df %>%
  filter(!foldID %in% c(19, 23, 21, 17, 8, 19))
```

@@

```{r}
scbi_cv_grid <- spatialBlock(
  speciesData = scbi_growth_df, theRange = 100, k = 28, yOffset = 0.9999, verbose = FALSE
)

# Add foldID to data
scbi_growth_df <- scbi_growth_df %>% 
  mutate(
    foldID = scbi_cv_grid$foldID
  )

# Visualize grid
scbi_cv_grid$plots +
  geom_sf(data = scbi_growth_df, aes(col=factor(foldID)), size = 0.1)
```

@@

Next we specify the growth model we want. We will model growth as a function of tree identity, size (in dbh), and the identity and size (in dbh) of its neighbors. The model can be run on different grouping of individuals (e.g., based on species or trait groupings). It can also be run with different notions of competition:

@@

```{r}
bw_specs <- bw_growth_df %>% 
  get_model_specs(model_number = 3, species_notion = 'trait_group')
bw_specs

scbi_specs <- scbi_growth_df %>% 
  get_model_specs(model_number = 3, species_notion = 'sp')
```

Next we create the `focal_vs_comp` data frame which connects each tree in `growth_df` to the trees in its competitive neighborhood range (as defined by `max_dist`). So for example, if `growth_df` consisted of two focal trees with two and three neighbors respectively, `focal_vs_comp` would consist of 5 rows.

This requires the `growth_df` data frame, `max_dist` scalar defining competitive range, `cv_fold_size` defining the size of the spatial cross-validation blocks, and `model_specs` as inputs.

```{r}
focal_vs_comp_bw <- bw_growth_df %>% 
  create_focal_vs_comp(max_dist, model_specs = bw_specs, cv_grid = bw_cv_grid, id = "treeID")
```

```{r}
glimpse(focal_vs_comp_bw)
```
